R Notebook

### 2023-01-05 Code/Simulation.Rmd
Small typo

# Create a master data_frame with all the results
histogram <- c(rep("Autoarma", n_tests), rep("Naive", n_tests))
p_values <- c(pvals_autoarma, pvals_naive)
results <- data_frame(p_values, histogram)

>>>>

# Create a master data_frame with all the results
histogram <- c(rep("Autoarma", nrep), rep("Naive", nrep))
p_values <- c(pvals_autoarma, pvals_naive)
results <- data_frame(p_values, histogram)
